Redundant calibration as a complex optimization problem

### 2017-01-09 paper.tex
added new info to the paper

\section{Results}
In this section we compare the computational complexity of two newly proposed speedup algorithms for redundant calibration, namely the ADI \citep{Marthi2014} and PCG \citep{Liu2010} methods. We restrict ourselves to comparing the most 
expensive operation of the two methods namely, computing the inverse of the Hessian $\bH$ (or modified Hessian $\bmH$ in the case of LM). It becomes trivial to rate these two 
algorithms relative to each other once the computational complexity of the inverse operation is known. The simulations we performed to compare these two 
methods are summarized in Section~\ref{sec:simulations}.

The basic difference between these two algorithms can be understood by inspecting Fig.~\ref{fig:hessian}. The first observation we can make by inspecting 
Fig.~\ref{fig:hessian_reg} and Fig.~\ref{fig:hessian_hex} is that the diagonal entries of the Hessians are more significant than the off-diagonal entries.
It therefore makes sense to approximate the Hessian (or the modified Hessian) with its diagonal, which greatly simplifies the computational complexity of inverting 
the Hessian, i.e. it becomes $\mathbb{O}(P)$\footnote{The cost of constructing 
the diagonal is not included in this estimate.} \citep{Smirnov2015}. This diagonal-approximation approach is effectively ADI \citep{Marthi2014}. The exact details of this 
approach is discussed in Section~\ref{sec:adi}. We will also show how \citet{Marthi2014}, \citet{Smirnov2015} and \citet{Salvini2014} relate to each other in that same section.

@@

In Section~\ref{sec:sbc} we briefly review the ADI method that is used for skymodel-based calibration. 
%In Section~\ref{sec:red} we show how the ADI method used for skymodel-based calibration relates to the redundant ADI method presented in \citet{Marthi2014}. 
In Section~\ref{sec:red}, we re-derive the ADI method presented in \citet{Marthi2014}. In \citet{Marthi2014} the ADI method is derived by taking the derivative of the 
objective function $\Lambda$ relative to $\bg$ and $\by$ and setting the result to naught. When derived in this way, its relation to the recent works \citep{Salvini2014,Smirnov2015} are unclear.
In Section~\ref{sec:red}, we use the diagonal-approximate approach proposed in \citet{Smirnov2015} to show that the ADI algorithm presented in \citet{Marthi2014} is in actual fact redundant 
\textsc{StEfCal} \citep{Salvini2014}.

@@

%\subsection{Diagonalization and StEFCal}
\subsubsection{Skymodel-based Calibration}
\label{sec:sbc}
\textsc{StEFCal} is an alternating direction implicit method, in which the measurement equation, Eq.~\eqref{eq:vis_definition}, is linearized by assuming that the gains are known, but
that their conjugates are unknown \citep{Mitchell:MWA-cal,Salvini2014}. Under this assumption, the conjugates of the gains can be obtained trivially. Once the conjugates of the gains have been computed, the gains can be solved for. One can then alternate between computing the gains and their conjugates until convergence
is reached. By correctly exploiting the symmetry inherent in the calibration problem this alternating approach can be replaced by a single iterative new parameter estimation step. \cite{Salvini2014} also show that
the convergence of the algorithm can be improved if for every even iteration the basic new parameter estimation step is modified as follows: the current gain estimate is replaced by the average of the current gain estimate and the gain estimate of the previous odd iteration.
\textsc{StEFCal} lowers the computational complexity of normal skymodel-based calibration from $\mathbb{O}(N^3)$ to $\mathbb{O}(N^2)$.

\citet{Smirnov2015} recently showed that one can also derive \textsc{StEFCal} by viewing normal skymodel-based calibration as a complex optimization problem. They first compute the skymodel-based calibration equivalent analytic expressions of $\bJ$,
$\bH$ and $\bJ^H\breve{\br}$. While inspecting the skymodel-based $\bH$ it becomes apparent that its diagonal entries are much more significant than its off-diagonal entries.
By approximating $\bH$ by its diagonal and substituting this approximate Hessian back into the GN update step they are able to re-derive the fundamental iterative StEFCal parameter estimation step. They then show that the 
averaging parmeter step used on even iterations can be derived by substituting the approximate $H$ into the LM update step, whilst setting $\lambda$ to one.

The StEFCal equivalent of Eq.~\eqref{eq:two_thrids}
is equal to \citep{Smirnov2015}
\begin{equation}
\label{eq:one_half}
\breve{\bg}_{k+1} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\bd} + \frac{1}{2}\breve{\bg}_{k}. 
\end{equation}
Note that in Eq.~\eqref{eq:one_half} the influence that the estimate of the parameters from the previous iteration has on the current iteration is scaled by a half, while
in Eq.~\eqref{eq:two_thrids} it is scaled by two thirds. Moreover, the diagonal-approximate iterative StEFCal estimation step is \citep{Smirnov2015}
\begin{align}
\breve{\bg}_{k+1} &\approx \frac{1}{1+\lambda}\widetilde{\bH}^{-1}\bJ^H\breve{\bd} + \frac{\lambda}{1+\lambda} \breve{\bg}_k,\label{eq:stef_lambda}\\
 &= \alpha \widetilde{\bH}^{-1}\bJ^H\breve{\bd} + (1-\alpha)\breve{\bg}_k, \label{eq:stef_alpha}  
\end{align}
where $\widetilde{\bH}$ denotes the diagonal approximation of $\bJ^H\bJ$, $\alpha = \frac{1}{1+\lambda}$. Moreover, $\lambda = \frac{1-\alpha}{\alpha}$.

On the odd iterations $\lambda$ is chosen to be zero, which corresponds to an $\alpha$ equal to one. On the even iteration $\lambda$ is chosen to be equal to one, which corresponds
to an $\alpha$ equal to a half. Note that, on the odd iteration the influence that the estimate of the parameters of the previous iteration has on the current estimate is scaled
by a half. Note the similarity between the last terms of Eq.~\eqref{eq:stef_alpha} and Eq.~\eqref{eq:one_half} when $\alpha$ is a half.

\subsubsection{Redundant Calibration}
\label{sec:red}
The natural question now arises: is it possible to derive a redundant calibration variant of the StEfCal algorithm if we follow a similar approach to what \citet{Smirnov2015}
proposed?

Inspecting Eq.~\eqref{eq:red_H} reveals that in the case of redundant calibration the Hessian's diagonal entries are also more significant than its off-diagonal entries.
If we substitute $\bJ^H\bJ$ with $\widetilde{\bH}$ (by its diagonal approximation) and replace $\breve{\br}$ with $\breve{\bd} - \breve{\bv}$ in Eq.~\eqref{eq:GN_update} we obtain
\begin{equation}
\label{eq:appr_GN}
 \Delta \breve{\bz} \approx \widetilde{\bH}^{-1}\bJ^H(\breve{\bd}-\breve{\bv})
\end{equation}
Utilizing the second identity in Eq.~\eqref{eq:identities} allows us to simplify Eq.~\eqref{eq:appr_GN} to
\begin{equation}
  \Delta \breve{\bz} \approx \widetilde{\bH}^{-1}\bJ^H\breve{\bd}-\breve{\bz}.
\end{equation}
It now trivially follows that
\begin{equation}
 \breve{\bz}_{k+1} \approx \widetilde{\bH}^{-1}\bJ^H\breve{\bd}.
\end{equation}
We obtain a similar result if we repeat the above procedure, only in this case we use Eq.~\eqref{eq:LM_update} instead,
namely
\begin{align}
\breve{\bz}_{k+1} &\approx \frac{1}{1+\lambda}\widetilde{\bH}^{-1}\bJ^H\breve{\bd} + \frac{\lambda}{1+\lambda} \breve{\bz}_k,\label{eq:lambda}\\
 &= \alpha \widetilde{\bH}^{-1}\bJ^H\breve{\bd} + (1-\alpha)\breve{\bz}_k. \label{eq:alpha}  
\end{align}
The analytic expression of $\bJ^H\breve{\bd}$ will be very similar to the analytic 
expression of $\bJ^H\breve{\br}$, the only difference being that in Eq.~\eqref{eq:ab} the letter $r$ would be replaced by a $d$. If we substitute the analytic expression
of $\bJ^H\breve{\bd}$ and $\widetilde{\bH}^{-1}$ (which is easily computed as the matrix is a diagonal matrix) into Eq.~\eqref{eq:alpha} we obtain the following two update rules:
\begin{equation}
\label{eq:g_update}
g_{i}^{k+1} = \alpha \frac{\sum_{j\neq i} g_j^k \widetilde{y}_{ij}^{~\!\!k} d_{ij}}{\sum_{j\neq i} |g_j^k|^2|y_{\zeta_{ij}}^k|^2} + (1-\alpha) g_i^k, 
\end{equation}
and
\begin{equation}
\label{eq:y_update}
y_{i}^{k+1} = \alpha \frac{\sum_{pq \in \mathcal{PQ}_i} \conj{g}_p^k g_q^k d_{pq}}{\sum_{pq \in \mathcal{PQ}_i}|g_p^k|^2|g_q^k|^2} + (1-\alpha) y_i^k. 
\end{equation}
The computational complexity of inverting $\widetilde{\bH}$ is $\mathbb{O}(P)$.

Eq.~\eqref{eq:g_update} and Eq.~\eqref{eq:y_update} are the exact same iterative new parameter estimators derived by \citet{Marthi2014}. Als note that Eq.~\eqref{eq:g_update} is the fundamental
iterative StEfCal new parameter estimator. We have therefore successfully used the diagonal approximation approach suggested by \citet{Smirnov2015} to re-derive the ADI method presented in 
\citet{Marthi2014} and in doing so we have shown that the algorithm in \citet{Marthi2014} is actually redundant StEfCal. We could also have shown this by using a similar approach 
to the one presented in \citet{Salvini2014}.

The question now arises what value should we use for $\alpha$? In \citet{Marthi2014} they propose 
$\alpha = 0.3$. Although an exact mathematical proof for the optimal choice of $\alpha$ still eludes us, it is still possible to
venture a clever guess by studying what the choice of $\alpha$ is in the case of skymodel-based StEFCal. Recall from Section~\ref{sec:sbc} that $\alpha$ is equal to a half 
in the case of StEFCal. If we wish to mimic this behaviour for the redundant calibration use case we need to scale $\breve{\bz}$ by two thirds in Eq.~\eqref{eq:alpha} (see Eq.~\eqref{eq:two_thrids}) which implies that we should choose $\alpha$ equal to a third, which corresponds to a $\lambda$ equal to two,
which is the value we used in this paper.

@@

The first order Taylor expansion of Eq.~\eqref{eq:lincal_vec} around the fiducial point $\bvarrho_0$ is equal to
\begin{equation}
\label{eq:d_lin}
\bd = \bv_0 + \bmJ_0 \Delta \bvarrho  + \bn.
\end{equation}
If we calculate the residual, dropping the reference to a specific fiducial point, we obtain: 
\begin{equation}
\label{eq:r_lin}
\br = \bd - \bv = \bmJ \Delta \bvarrho + \bn.
\end{equation}
Moreover,
\begin{equation}
\label{eq:jac_upper_lincal}
\bmJ = \begin{bmatrix}
       \bN & \bM 
       \end{bmatrix},
\end{equation}
where
\begin{align}
\bN &= \begin{bmatrix} \bO & \bP \end{bmatrix}, & \bM &= \begin{bmatrix} \bQ & \bR \end{bmatrix}, 
\end{align}
\begin{equation}
 [\bO]_{\alpha_{pq},j} =  \frac{\partial v_{pq}}{\partial \eta_j} = \begin{cases} 
    v_{pq} &\textrm{if}~(p=j)~\textrm{or}~(q=j)\\
    0 & \textrm{otherwise}
   \end{cases},
\end{equation}
\begin{equation}
 [\bP]_{\alpha_{pq},j} =  \frac{\partial v_{pq}}{\partial \varphi_j} = \begin{cases}
                                                                        i v_{pq} &\textrm{if}~ p=j\\
                                                                        -i v_{pq} &\textrm{if}~ q=j \\
                                                                        0 & \textrm{otherwise} 
                                                                       \end{cases}
\end{equation}
\begin{equation}
 [\bQ]_{\alpha_{pq},j} =  \frac{\partial v_{pq}}{\partial \widetilde{\eta}_j} = \begin{cases} 
    v_{pq} &\textrm{if}~\phi_{pq}=j\\
    0 & \textrm{otherwise}
   \end{cases},
\end{equation}
\begin{equation}
 [\bR]_{\alpha_{pq},j} =  \frac{\partial v_{pq}}{\partial \widetilde{\varphi}_j} = \begin{cases} 
    i v_{pq} &\textrm{if}~\phi_{pq}=j\\
    0 & \textrm{otherwise}
   \end{cases}.
\end{equation}
Augmenting the residual by taking into account its conjugate results in 
\begin{equation}
\breve{\br} = \bJ \Delta \bvarrho + \bn, 
\end{equation}
where $\breve{\br} = \begin{bmatrix}\br^T & \conj{\br}^T \end{bmatrix}^T$ and 
\begin{equation}
\label{eq:Jac_lin}
\bJ = 
\begin{bmatrix}
 \bmJ\\  
 \conj{\bmJ}
\end{bmatrix}.
\end{equation}
The solution to 
\begin{equation}
 \min_{\Delta \bvarrho} \| \breve{\br} - \bJ \Delta \bvarrho\|_F^2,
\end{equation}
is equal to 
\begin{equation}
\label{eq:LINCAL_update}
\Delta \bvarrho = (\bJ^H\bJ)^{-1} \bJ^H\breve{\br}. 
\end{equation}
Eq.~\eqref{eq:LINCAL_update} is used to iteratively determine a new estimate of the parameter vector $\bvarrho$ as follows
\begin{equation}
\label{eq:new_rho}
\bvarrho_{k+1} = \bvarrho_k + \Delta \bvarrho_k. 
\end{equation}
Note that we do not explicitly denote the $k$ index in Eq.~\eqref{eq:LINCAL_update}. We update our parameter vector until convergence is reached.   
\label{lastpage}
\end{document}

>>>>

\section{Results}
\label{sec:results}
In this section we compare the computational complexity of two newly proposed speedup algorithms for redundant calibration, namely the ADI \citep{Marthi2014} and PCG \citep{Liu2010} methods. We restrict ourselves to comparing the most 
expensive operation of the two methods namely, computing the inverse of the Hessian $\bH$ (or modified Hessian $\bmH$ in the case of LM). It becomes trivial to rate these two 
algorithms relative to each other once the computational complexity of the inverse operation is known. The simulations we performed to compare these two 
methods are summarized in Section~\ref{sec:simulations}.

The basic difference between these two algorithms can be understood by inspecting Fig.~\ref{fig:hessian}. The first observation we can make by inspecting 
Fig.~\ref{fig:hessian_reg} and Fig.~\ref{fig:hessian_hex} is that the diagonal entries of the Hessians are more significant than the off-diagonal entries.
It therefore makes sense to approximate the Hessian (or the modified Hessian) with its diagonal, which greatly simplifies the computational complexity of inverting 
the Hessian, i.e. it becomes $\mathbb{O}(P)$\footnote{The cost of constructing 
the diagonal is not included in this estimate.} \citep{Smirnov2015}. This diagonal-approximation approach is effectively ADI \citep{Marthi2014}. The exact details of this 
approach is discussed in Section~\ref{sec:adi}. We will also show how \citet{Marthi2014}, \citet{Smirnov2015} and \citet{Salvini2014} relate to each other in that same section. In Appendix~\ref{sec:sbc} we briefly summarize the ADI method that is used for skymodel-based calibration.

@@

%In Section~\ref{sec:adi} we show how the ADI method used for skymodel-based calibration relates to the redundant ADI method presented in \citet{Marthi2014}. 
In this section we re-derive the ADI method presented in \citet{Marthi2014}. In \citet{Marthi2014} the ADI method is derived by taking the derivative of the 
objective function $\Lambda$ relative to $\bg$ and $\by$ and setting the result to naught. When derived in this way, its relation to the recent works \citep{Salvini2014,Smirnov2015} are unclear.
We will use the diagonal-approximate approach proposed in \citet{Smirnov2015} to show that the ADI algorithm presented in \citet{Marthi2014} is in actual fact redundant 
\textsc{StEfCal} \citep{Salvini2014}. Perusing through Appendix~\ref{sec:sbc} is advised before continuing this section.

As we mention in Section~\ref{sec:results}, inspecting Fig.~\ref{fig:hessian} (also see Eq.~\eqref{eq:red_H}) reveals that in the case of redundant calibration the Hessian's diagonal entries are more significant than its off-diagonal entries.
If we substitute $\bJ^H\bJ$ with $\widetilde{\bH}$ (by its diagonal approximation) and replace $\breve{\br}$ with $\breve{\bd} - \breve{\bv}$ in Eq.~\eqref{eq:GN_update} we obtain
\begin{equation}
\label{eq:appr_GN}
 \Delta \breve{\bz} \approx \widetilde{\bH}^{-1}\bJ^H(\breve{\bd}-\breve{\bv})
\end{equation}
Utilizing the second identity in Eq.~\eqref{eq:identities} allows us to simplify Eq.~\eqref{eq:appr_GN} to
\begin{equation}
  \Delta \breve{\bz} \approx \widetilde{\bH}^{-1}\bJ^H\breve{\bd}-\breve{\bz}.
\end{equation}
It now trivially follows that
\begin{equation}
 \breve{\bz}_{k+1} \approx \widetilde{\bH}^{-1}\bJ^H\breve{\bd}.
\end{equation}
We obtain a similar result if we repeat the above procedure, only in this case we use Eq.~\eqref{eq:LM_update} instead,
namely
\begin{align}
\breve{\bz}_{k+1} &\approx \frac{1}{1+\lambda}\widetilde{\bH}^{-1}\bJ^H\breve{\bd} + \frac{\lambda}{1+\lambda} \breve{\bz}_k,\label{eq:lambda}\\
 &= \alpha \widetilde{\bH}^{-1}\bJ^H\breve{\bd} + (1-\alpha)\breve{\bz}_k, \label{eq:alpha}  
\end{align}
where $\alpha = \frac{1}{1+\lambda}$. Moreover, $\lambda = \frac{1-\alpha}{\alpha}$.
The analytic expression of $\bJ^H\breve{\bd}$ will be very similar to the analytic 
expression of $\bJ^H\breve{\br}$, the only difference being that in Eq.~\eqref{eq:ab} the letter $r$ would be replaced by a $d$. If we substitute the analytic expression
of $\bJ^H\breve{\bd}$ and $\widetilde{\bH}^{-1}$ (which is easily computed as the matrix is a diagonal matrix) into Eq.~\eqref{eq:alpha} we obtain the following two update rules:
\begin{equation}
\label{eq:g_update}
g_{i}^{k+1} = \alpha \frac{\sum_{j\neq i} g_j^k \widetilde{y}_{ij}^{~\!\!k} d_{ij}}{\sum_{j\neq i} |g_j^k|^2|y_{\zeta_{ij}}^k|^2} + (1-\alpha) g_i^k, 
\end{equation}
and
\begin{equation}
\label{eq:y_update}
y_{i}^{k+1} = \alpha \frac{\sum_{pq \in \mathcal{PQ}_i} \conj{g}_p^k g_q^k d_{pq}}{\sum_{pq \in \mathcal{PQ}_i}|g_p^k|^2|g_q^k|^2} + (1-\alpha) y_i^k. 
\end{equation}
The computational complexity of inverting $\widetilde{\bH}$ is $\mathbb{O}(P)$.

Eq.~\eqref{eq:g_update} and Eq.~\eqref{eq:y_update} are the exact same iterative new parameter estimators derived by \citet{Marthi2014}. Als note that Eq.~\eqref{eq:g_update} is the fundamental
gain estimator associated with StEfCal. We have therefore successfully used the diagonal approximation approach suggested by \citet{Smirnov2015} to re-derive the ADI method presented in 
\citet{Marthi2014} and in doing so we have shown that the algorithm in \citet{Marthi2014} is actually redundant StEfCal. We could also have shown this by using a similar approach 
to the one presented in \citet{Salvini2014}.

The question now arises what value should we use for $\alpha$? In \citet{Marthi2014} they propose 
$\alpha = 0.3$. Although an exact mathematical proof for the optimal choice of $\alpha$ still eludes us, it is still possible to
venture a clever guess by studying what the choice of $\alpha$ is in the case of skymodel-based StEFCal. Recall from Section~\ref{sec:sbc} that $\alpha$ is equal to a half 
in the case of StEFCal (for even iterations). If we wish to mimic this behaviour for the redundant calibration use case we need to scale $\breve{\bz}$ by two thirds in Eq.~\eqref{eq:alpha} (see Eq.~\eqref{eq:two_thrids}) which implies that we should choose $\alpha$ equal to a third, which corresponds to a $\lambda$ equal to two.
We used $\lambda$ equal to two in this paper.

@@

@@

The first order Taylor expansion of Eq.~\eqref{eq:lincal_vec} around the fiducial point $\bvarrho_0$ is equal to
\begin{equation}
\label{eq:d_lin}
\bd = \bv_0 + \bmJ_0 \Delta \bvarrho  + \bn.
\end{equation}
If we calculate the residual, dropping the reference to a specific fiducial point, we obtain: 
\begin{equation}
\label{eq:r_lin}
\br = \bd - \bv = \bmJ \Delta \bvarrho + \bn.
\end{equation}
Moreover,
\begin{equation}
\label{eq:jac_upper_lincal}
\bmJ = \begin{bmatrix}
       \bN & \bM 
       \end{bmatrix},
\end{equation}
where
\begin{align}
\bN &= \begin{bmatrix} \bO & \bP \end{bmatrix}, & \bM &= \begin{bmatrix} \bQ & \bR \end{bmatrix}, 
\end{align}
\begin{equation}
 [\bO]_{\alpha_{pq},j} =  \frac{\partial v_{pq}}{\partial \eta_j} = \begin{cases} 
    v_{pq} &\textrm{if}~(p=j)~\textrm{or}~(q=j)\\
    0 & \textrm{otherwise}
   \end{cases},
\end{equation}
\begin{equation}
 [\bP]_{\alpha_{pq},j} =  \frac{\partial v_{pq}}{\partial \varphi_j} = \begin{cases}
                                                                        i v_{pq} &\textrm{if}~ p=j\\
                                                                        -i v_{pq} &\textrm{if}~ q=j \\
                                                                        0 & \textrm{otherwise} 
                                                                       \end{cases}
\end{equation}
\begin{equation}
 [\bQ]_{\alpha_{pq},j} =  \frac{\partial v_{pq}}{\partial \widetilde{\eta}_j} = \begin{cases} 
    v_{pq} &\textrm{if}~\phi_{pq}=j\\
    0 & \textrm{otherwise}
   \end{cases},
\end{equation}
\begin{equation}
 [\bR]_{\alpha_{pq},j} =  \frac{\partial v_{pq}}{\partial \widetilde{\varphi}_j} = \begin{cases} 
    i v_{pq} &\textrm{if}~\phi_{pq}=j\\
    0 & \textrm{otherwise}
   \end{cases}.
\end{equation}
Augmenting the residual by taking into account its conjugate results in 
\begin{equation}
\breve{\br} = \bJ \Delta \bvarrho + \bn, 
\end{equation}
where $\breve{\br} = \begin{bmatrix}\br^T & \conj{\br}^T \end{bmatrix}^T$ and 
\begin{equation}
\label{eq:Jac_lin}
\bJ = 
\begin{bmatrix}
 \bmJ\\  
 \conj{\bmJ}
\end{bmatrix}.
\end{equation}
The solution to 
\begin{equation}
 \min_{\Delta \bvarrho} \| \breve{\br} - \bJ \Delta \bvarrho\|_F^2,
\end{equation}
is equal to 
\begin{equation}
\label{eq:LINCAL_update}
\Delta \bvarrho = (\bJ^H\bJ)^{-1} \bJ^H\breve{\br}. 
\end{equation}
Eq.~\eqref{eq:LINCAL_update} is used to iteratively determine a new estimate of the parameter vector $\bvarrho$ as follows
\begin{equation}
\label{eq:new_rho}
\bvarrho_{k+1} = \bvarrho_k + \Delta \bvarrho_k. 
\end{equation}
Note that we do not explicitly denote the $k$ index in Eq.~\eqref{eq:LINCAL_update}. We update our parameter vector until convergence is reached.

\section{Skymodel-based Calibration}
\label{sec:sbc}
\textsc{StEFCal} is an alternating direction implicit method, in which the measurement equation, Eq.~\eqref{eq:vis_definition}, is linearized by assuming that the gains are known, but
that their conjugates are unknown \citep{Mitchell:MWA-cal,Salvini2014}. Under this assumption, the conjugates of the gains can be obtained trivially. Once the conjugates of the gains have been computed, the gains can be solved for. One can then alternate between computing the gains and their conjugates until convergence
is reached. By correctly exploiting the symmetry inherent in the calibration problem this alternating approach can be replaced by a single iterative new parameter estimation step. \cite{Salvini2014} also show that
the convergence of the algorithm can be improved if for every even iteration the basic new parameter estimation step is modified as follows: the current gain estimate is replaced by the average of the current gain estimate and the gain estimate of the previous odd iteration.
\textsc{StEFCal} lowers the computational complexity of normal skymodel-based calibration from $\mathbb{O}(N^3)$ to $\mathbb{O}(N^2)$.

\citet{Smirnov2015} recently showed that one can also derive \textsc{StEFCal} by viewing normal skymodel-based calibration as a complex optimization problem.
As in the redundant use case depicted in Fig.~\ref{fig:hessian}, when we inspect the skymodel-based $\bH$ it becomes apparent that its diagonal entries are much more significant than its off-diagonal entries.
By approximating $\bH$ by its diagonal and substituting this approximate Hessian $\widetilde{\bH}$ back into the fundamental skymodel-based LM update step we obtain \citep{Smirnov2015} 
\begin{align}
\breve{\bg}_{k+1} &\approx \frac{1}{1+\lambda}\widetilde{\bH}^{-1}\bJ^H\breve{\bd} + \frac{\lambda}{1+\lambda} \breve{\bg}_k,\label{eq:stef_lambda}\\
 &= \alpha \widetilde{\bH}^{-1}\bJ^H\breve{\bd} + (1-\alpha)\breve{\bg}_k, \label{eq:stef_alpha}  
\end{align}

If we choose $\lambda$ to be zero, which corresponds to an $\alpha$ equal to one, we obtain the new parameter estimation step of \textsc{StEfCal}; used during odd iterations. On the other hand if we choose $\lambda$ equal to one, which corresponds
to an $\alpha$ equal to a half, we obtain the new parameter estimation step of \textsc{StEfCal}; used during even iterations.

Furthermore, the simplified skymodel-based GN equivalent of Eq.~\eqref{eq:two_thrids} is equal to
\citep{Smirnov2015}
\begin{equation}
\label{eq:one_half}
\breve{\bg}_{k+1} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\bd} + \frac{1}{2}\breve{\bg}_{k}. 
\end{equation}
Note that in Eq.~\eqref{eq:one_half} the influence that the estimate of the parameters from the previous iteration has on the current iteration is scaled by a half, while
in Eq.~\eqref{eq:two_thrids} it is scaled by two thirds. Note the similarity between the last terms of Eq.~\eqref{eq:stef_alpha} and Eq.~\eqref{eq:one_half} when $\alpha$ is a half.

\label{lastpage}
\end{document}
